A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-07 survey.tex
(Flo) Add my bio.

>>>>

\begin{IEEEbiographynophoto}{Florian Richoux}
  is an associate  professor at the Laboratory of  Computer Science of
  the University of Nantes,  France.  His main research field concerns
  parallel  algorithms for solving  constraint-based problems  and has
  strong  interests   in  AI,  in  particular  game   AI  and  machine
  learning. He  obtained his Ph.D. in Theoretical  Computer Science at
  the {\'E}cole Polytechnique  in 2009 and has been  for three years a
  CNRS   research  fellow  at   the  Japanese-French   Laboratory  for
  Informatics of the University of Tokyo, Japan.
\end{IEEEbiographynophoto}
